Homework 3: The Florentine Wedding dataset

### 2022-02-10 _academics/ps753-hw3/ps753-hw3.Rmd
tidy code

plot(ntwk.ig, layout = layout_in_circle(ntwk.ig), edge.arrow.mode = 0, vertex.label.color="black", vertex.shape = "circle", vertex.label.font = 2, main = "Florence interfamily marriages, 1282-1500")
```

@@

```{r}
set.seed(1235)
V(ntwk.ig)$size <- ntwk.nodes[,"degree"] * 3
plot(ntwk.ig, layout = layout_components(ntwk.ig), edge.arrow.mode = 0, vertex.label.color="black", vertex.shape = "circle", vertex.label.font = 2, main = "Florence interfamily marriages, 1282-1500")

>>>>

plot(
  ntwk.ig,
  layout = layout_in_circle(ntwk.ig),
  edge.arrow.mode = 0,
  vertex.label.color = "black",
  vertex.shape = "circle",
  vertex.label.font = 2,
  main = "Florence interfamily marriages, 1282-1500"
)
```

@@

```{r}
set.seed(1235)
V(ntwk.ig)$size <- ntwk.nodes[,"degree"] * 3
plot(
  ntwk.ig,
  layout = layout_components(ntwk.ig),
  edge.arrow.mode = 0,
  vertex.label.color = "black",
  vertex.shape = "circle",
  vertex.label.font = 2,
  main = "Florence interfamily marriages, 1282-1500"
)
